timesliced_random_cell_selection

### 2018-11-26 src/data_exploration.Rmd
background env correlate histograms

Read in the presence points

@@

# Update: Who sampled in which year and which month:

@@

@@

#simple plots of env. correlates

@@

# simple boxplots of env. corr

@@

XXX SAM YOU WANT TO PUT THE TWO LAYERS ON THE ONE PLOT - NOT TWO SIDE BY SIDE

@@

>>>>

# presence points
Read in the presence points

@@

## Update: Who sampled in which year and which month:

@@

## environmental correlates

@@

## simple plots of env. correlates

@@

## simple boxplots of env. corr

@@

@@

# background points
Read in the presence points

```{r}
background <- read.csv("../output/bio/background_complete_obs_cels.csv", header = TRUE)
head(background)
```

Temperature
```{r}
temp_depth_max_back <- max(background$temp_depth, na.rm = TRUE)
temp_depth_min_back <- min(background$temp_depth, na.rm = TRUE)
temp_depth_mean_back <- mean(background$temp_depth, na.rm = TRUE)
temp_surface_max_back <- max(background$temp_surface, na.rm = TRUE)
temp_surface_min_back <- min(background$temp_surface, na.rm = TRUE)
temp_surface_mean_back <- mean(background$temp_surface, na.rm = TRUE)
```

Salinity
```{r}
sal_depth_max_back <- max(background$salinity_depth, na.rm = TRUE)
sal_depth_min_back <- min(background$salinity_depth, na.rm = TRUE)
sal_depth_mean_back <- mean(background$salinity_depth, na.rm = TRUE)
sal_surface_max_back <- max(background$salinity_surface, na.rm = TRUE)
sal_surface_min_back <- min(background$salinity_surface, na.rm = TRUE)
sal_surface_mean_back <- mean(background$salinity_surface, na.rm = TRUE)
```

Chl
```{r}
chl_depth_max_back <- max(background$chl_depth, na.rm = TRUE)
chl_depth_min_back <- min(background$chl_depth, na.rm = TRUE)
chl_depth_mean_back <- mean(background$chl_depth, na.rm = TRUE)
chl_surface_max_back <- max(background$chl_surface, na.rm = TRUE)
chl_surface_min_back <- min(background$chl_surface, na.rm = TRUE)
chl_surface_mean_back <- mean(background$chl_surface, na.rm = TRUE)
```

O2
```{r}
o2_depth_max_back <- max(background$o2_depth, na.rm = TRUE)
o2_depth_min_back <- min(background$o2_depth, na.rm = TRUE)
o2_depth_mean_back <- mean(background$o2_depth, na.rm = TRUE)
o2_surface_max_back <- max(background$o2_surface, na.rm = TRUE)
o2_surface_min_back <- min(background$o2_surface, na.rm = TRUE)
o2_surface_mean_back <- mean(background$o2_surface, na.rm = TRUE)
```

MLP
```{r}
mlp_surface_max_back <- max(background$mlp_surface, na.rm = TRUE)
mlp_surface_min_back <- min(background$mlp_surface, na.rm = TRUE)
mlp_surface_mean_back <- mean(background$mlp_surface, na.rm = TRUE)
```

SSH
```{r}
ssh_surface_max_back <- max(background$ssh_surface, na.rm = TRUE)
ssh_surface_min_back <- min(background$ssh_surface, na.rm = TRUE)
ssh_surface_mean_back <- mean(background$ssh_surface, na.rm = TRUE)
```

create matrix
```{r}
tdb <- c(temp_depth_max_back, temp_depth_min_back, temp_depth_mean_back)
tsb <- c(temp_surface_max_back, temp_surface_min_back, temp_surface_mean_back)
sdb <- c(sal_depth_max_back, sal_depth_min_back, sal_depth_mean_back)
ssb <- c(sal_surface_max_back, sal_surface_min_back, sal_surface_mean_back)
cdb <- c(sal_depth_max_back, sal_depth_min_back, sal_depth_mean_back)
csb <- c(sal_surface_max_back, sal_surface_min_back, sal_surface_mean_back)
odb <- c(o2_depth_max_back, o2_depth_min_back, o2_depth_mean_back)
osb <- c(o2_surface_max_back, o2_surface_min_back, o2_surface_mean_back)
mlpb <- c(mlp_surface_max_back, mlp_surface_min_back, mlp_surface_mean_back)
sshb <- c(ssh_surface_max_back, ssh_surface_min_back, ssh_surface_mean_back)
env_stats_back <- rbind(tdb, tsb, sdb, ssb, cdb, csb, odb, osb, mlpb, sshb)
row.names(env_stats_back) <- c("Temp Depth", "Temp Surface", "Salinity Depth", "Salinity Surface", "Chl Depth", "Chl Surface", "Oxygen Depth", "Oxygen Surface", "MLP", "SSH") 
colnames(env_stats_back) <- c("Max", "Min", "Mean")
write.csv(env_stats_back, "../output/env/env_correlates_background_basic_stats.csv", row.names = TRUE)
env_stats_back
```

### 2018-11-26 src/timesliced_random_cell_selection.Rmd
background env correlate histograms

create a new column for Occurence, and populate with "0" (because these are all background)
```{r}
background_all$occurrence <- "0"
write.csv(background_all, "../output/bio/background_complete_obs.csv", row.names = FALSE)
head(background_all)
```

>>>>

create a new column for Occurence, and populate with "0" (because these are all background)
```{r}
background_all <- read.csv("../output/bio/background_complete.csv")
background_all$occurrence <- "0"
write.csv(background_all, "../output/bio/background_complete_obs.csv", row.names = FALSE)
head(background_all)
```
